Human Judgement Forecasting of COVID-19 in the UK

### 2023-03-28 manuscript/manuscript.tex
Updates from Overleaf

>>>>

An median ensemble of two week ahead forecasts made only by "experts" or "non-experts" performed worse than the combined crowd example, both for cases and deaths and both on the log scale and on the natural scale (see Table \ref{tab:scores-experts}).

For cases two week ahead, "experts" achieved better scores than "non-experts" both on the log and on the natural scale. WIS values \textit{relative to the combined crowd ensemble} were 1.08 for "experts" and 1.14 for "non-experts" on the log scale and 1.03 for "experts" and 1.14 for "non-experts" on the natural scale.
